\class : Problem Set \psetnum

### 2022-05-11 531_stars/pset4/solutions.tex
not sure on Q2 stars HW4

\question{\textbf{23.2 - Central Temperature-Density Gradient}}
\answer{}

>>>>

\question{\textbf{23.2 - Central Temperature-Density Gradient}}
\answer{
    The evolution of a star in the $T_c$--$\rho_c$ diagram becomes less steep at late evolution phases. This means that for a given increase in density, the increase in temperature is not as strong.
    \todo{I think this is probably something to do with the mass defect being lower and so the energy/temperature production is lower?}
}
